New cardinality estimation algorithms for HyperLogLog sketches

### 2016-09-12 paper/paper.tex
number formatting in tables

\sisetup{
fixed-exponent = 2,
scientific-notation = fixed,
}

@@

\begin{table}
\centering
\caption{The list of cases for which the cardinalities $|\symSetA|$, $|\symSetB|$, and $|\symSetX|$ have been estimated given two HyperLogLog sketches with parameters $\symPrecision=20$ and $\symRegRange=44$ representing $\symSetA\cup\symSetX$ and  $\symSetB\cup\symSetX$, respectively.}
\label{tbl:joint_estimation_cases}
\csvreader[before reading=\footnotesize, tabular=r|r|r|r|r|r, table head=\# & $|\symSetA|$ & $|\symSetB|$ & $|\symSetX|$ & $\frac{|\symSetX|}{|\symSetA\cup\symSetB\cup\symSetX|}$ & $\log_{10}\!\left(\frac{|\symSetA\cup\symSetX|}{|\symSetB\cup\symSetX|}\right)$\\\hline]
{intersection.csv}{trueCardA=\trueCardA,trueCardB=\trueCardB,trueCardX=\trueCardX,trueJaccardIdx=\trueJaccardIdx ,trueLogRatio=\trueLogRatio}{
\thecsvrow & \trueCardA & \trueCardB & \trueCardX & \trueJaccardIdx & \trueLogRatio
}
\end{table}

\begin{table}
\centering
\caption{The mean and the standard deviation for the cases given in \cref{tbl:joint_estimation_cases} when estimating $|\symSetA|$ using the inclusion-exlusion (IE) principle and the maximum likelihood method (ML), respectively.}
\label{tbl:joint_estimation_a}
\csvreader[before reading=\footnotesize, tabular=r|r|r|r|r, table head=\# & IE mean & IE stdev & ML mean & ML stdev\\\hline]
{intersection.csv}{inclExclMeanA=\inclExclMeanA,inclExclStdDevA=\inclExclStdDevA,
maxLikeMeanA=\maxLikeMeanA,maxLikeStdDevA=\maxLikeStdDevA}{
\thecsvrow & \inclExclMeanA & \inclExclStdDevA & \maxLikeMeanA & \maxLikeStdDevA
}
\end{table}

\begin{table}
\centering
\caption{The mean and the standard deviation for the cases given in \cref{tbl:joint_estimation_cases} when estimating $|\symSetB|$ using the inclusion-exlusion (IE) principle and the maximum likelihood method (ML), respectively.}
\label{tbl:joint_estimation_b}
\csvreader[before reading=\footnotesize, tabular=r|r|r|r|r, table head=\# & IE mean & IE stdev & ML mean & ML stdev\\\hline]
{intersection.csv}{inclExclMeanB=\inclExclMeanB,inclExclStdDevB=\inclExclStdDevB,
maxLikeMeanB=\maxLikeMeanB,maxLikeStdDevB=\maxLikeStdDevB}{
\thecsvrow & \inclExclMeanB & \inclExclStdDevB & \maxLikeMeanB & \maxLikeStdDevB
}
\end{table}

\begin{table}
\centering
\caption{The mean and the standard deviation for the cases given in \cref{tbl:joint_estimation_cases} when estimating $|\symSetX|$ using the inclusion-exlusion (IE) principle and the maximum likelihood method (ML), respectively.}
\label{tbl:joint_estimation_x}
\csvreader[before reading=\footnotesize, tabular=r|r|r|r|r, table head=\# & IE mean & IE stdev & ML mean & ML stdev\\\hline]
{intersection.csv}{inclExclMeanX=\inclExclMeanX,inclExclStdDevX=\inclExclStdDevX,
maxLikeMeanX=\maxLikeMeanX,maxLikeStdDevX=\maxLikeStdDevX}{
\thecsvrow & \inclExclMeanX & \inclExclStdDevX & \maxLikeMeanX & \maxLikeStdDevX
}
\end{table}

>>>>

@@

\begin{table}
\centering
\caption{The list of cases for which the cardinalities $|\symSetA|$, $|\symSetB|$, and $|\symSetX|$ have been estimated given two HyperLogLog sketches with parameters $\symPrecision=20$ and $\symRegRange=44$ representing $\symSetA\cup\symSetX$ and  $\symSetB\cup\symSetX$, respectively.}
\label{tbl:joint_estimation_cases}
\csvreader[before reading=\footnotesize, tabular=r|r|r|r|r|r, table head=\# & $|\symSetA|$ & $|\symSetB|$ & $|\symSetX|$ & $\frac{|\symSetX|}{|\symSetA\cup\symSetB\cup\symSetX|}$ & $\log_{10}\!\left(\frac{|\symSetA\cup\symSetX|}{|\symSetB\cup\symSetX|}\right)$\\\hline]
{intersection.csv}{trueCardA=\trueCardA,trueCardB=\trueCardB,trueCardX=\trueCardX,trueJaccardIdx=\trueJaccardIdx ,trueLogRatio=\trueLogRatio}{
\thecsvrow & 
\num{\trueCardA} & 
\num{\trueCardB} & 
\num{\trueCardX} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\trueJaccardIdx} & 
\num[scientific-notation = fixed,round-mode = places,round-precision = 3]{\trueLogRatio}
}
\end{table}

\begin{table}
\centering
\caption{The mean and the standard deviation for the cases given in \cref{tbl:joint_estimation_cases} when estimating $|\symSetA|$ using the inclusion-exlusion (IE) principle and the maximum likelihood method (ML), respectively.}
\label{tbl:joint_estimation_a}
\csvreader[before reading=\footnotesize, tabular=r|r|r|r|r, table head=\# & IE mean & IE stdev & ML mean & ML stdev\\\hline]
{intersection.csv}{inclExclMeanA=\inclExclMeanA,inclExclStdDevA=\inclExclStdDevA,
maxLikeMeanA=\maxLikeMeanA,maxLikeStdDevA=\maxLikeStdDevA}{
\thecsvrow & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\inclExclMeanA} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\inclExclStdDevA} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\maxLikeMeanA} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\maxLikeStdDevA}
}
\end{table}

\begin{table}
\centering
\caption{The mean and the standard deviation for the cases given in \cref{tbl:joint_estimation_cases} when estimating $|\symSetB|$ using the inclusion-exlusion (IE) principle and the maximum likelihood method (ML), respectively.}
\label{tbl:joint_estimation_b}
\csvreader[before reading=\footnotesize, tabular=r|r|r|r|r, table head= {\#} & {IE mean} & {IE stdev} & {ML mean} & {ML stdev}\\\hline]
{intersection.csv}{inclExclMeanB=\inclExclMeanB,inclExclStdDevB=\inclExclStdDevB,
maxLikeMeanB=\maxLikeMeanB,maxLikeStdDevB=\maxLikeStdDevB}{
\thecsvrow & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\inclExclMeanB} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\inclExclStdDevB} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\maxLikeMeanB} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\maxLikeStdDevB}
}

\end{table}

\begin{table}
\centering
\caption{The mean and the standard deviation for the cases given in \cref{tbl:joint_estimation_cases} when estimating $|\symSetX|$ using the inclusion-exlusion (IE) principle and the maximum likelihood method (ML), respectively.}
\label{tbl:joint_estimation_x}
\csvreader[before reading=\footnotesize, tabular=r|r|r|r|r, table head=\# & IE mean & IE stdev & ML mean & ML stdev\\\hline]
{intersection.csv}{inclExclMeanX=\inclExclMeanX,inclExclStdDevX=\inclExclStdDevX,
maxLikeMeanX=\maxLikeMeanX,maxLikeStdDevX=\maxLikeStdDevX}{
\thecsvrow & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\inclExclMeanX} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\inclExclStdDevX} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\maxLikeMeanX} & 
\num[scientific-notation = true,round-mode = places,round-precision = 3]{\maxLikeStdDevX}
}
\end{table}
